\huspacy: an industrial-strength Hungarian natural language processing toolkit

### 2022-01-05 mszny2022/main.tex
Preprint v1

\author{György Orosz\inst{1,2} \and
    Zsolt Szántó\inst{1,2} \and \break
    Péter Berkecz\inst{1,2} \and
    Gergő Szabó\inst{1,2} \and
    Farkas Richárd\inst{1,2}\\
    \institute{
        $^1$Artificial Intelligence National Laboratory \break
        $^2$Institute of Informatics, University of Szeged\break
        Szeged Árpád tér 2., H-6720
    }
    \email{gyorgy@orosz.link}\break
    \email{\{szantozs,rfarkas\}@inf.u-szeged.hu}\break
    \email{\{berkecz.peter,szabogergo.a\}@gmail.com}\break
}

@@

We present \huspacy{}, a new industry-ready Hungarian natural language processing toolkit\footnote{We implemented our pipeline in spaCy v3.x. Prior to this work, there were attempts (\url{https://github.com/oroszgy/spacy-hungarian-models}) to support Hungarian in this framework, but none of those releases are compatible with the tool’s current version.}. 
It provides all the aforementioned basic text processing modules with high accuracy. The underlying models are optimized to be light on memory consumption and CPU usage. The presented tool is open source\footnote{\url{https://github.com/oroszgy/spacy-hungarian-models}} and is available under the permissive CC-BY-SA-4.0 license. Our system is built on top of spaCy’s infrastructure, thus extensive documentation, debugging tools, an ergonomic API and a flourishing ecosystem are already provided.

@@

% \section*{Acknowledgements}
% \label{Koszonet}

% ---- Bibliography ----
%
%kulon bibtex fajl hasznalata
\renewcommand\bibname{\refname}
\renewcommand\bibname{References}
%for papers written in English
\bibliographystyle{splncsnat_en}
\bibliography{references}

>>>>

\author{
György Orosz,
Zsolt Szántó, \break
Péter Berkecz,
Gergő Szabó,
Richárd Farkas\\
\institute{
    Institute of Informatics, University of Szeged\break
    Szeged, Árpád tér 2., H-6720\\
}
\email{gyorgy@orosz.link}\break
\email{\{szantozs,rfarkas\}@inf.u-szeged.hu}\break
}

@@

We present \huspacy{}, a new industry-ready Hungarian natural language processing toolkit\footnote{We implemented our pipeline in spaCy v3.x. Prior to this work, there were attempts (\url{https://github.com/oroszgy/spacy-hungarian-models}) to support Hungarian in this framework, but none of those releases are compatible with the tool’s current version.}. 
It provides all the aforementioned basic text processing modules with high accuracy. The underlying models are optimized to be light on memory consumption and CPU usage. The presented tool is open source\footnote{\url{https://github.com/huspacy/huspacy}} and is available under the permissive CC-BY-SA-4.0 license. Our system is built on top of spaCy’s infrastructure, thus extensive documentation, debugging tools, an ergonomic API and a flourishing ecosystem are already provided.

@@

\section*{Acknowledgements}
%\label{Koszonet}
HuSpaCy research and developments has been financed by the Ministry of Innovation and Technology NRDI Office within the framework of the Artificial Intelligence National Laboratory Program.

% ---- Bibliography ----
%
%kulon bibtex fajl hasznalata
\renewcommand\bibname{\refname}
\renewcommand\bibname{References}
%for papers written in English
\bibliographystyle{splncsnat_en}
\bibliography{main}
